Bayesian exponential random graph modeling of KWL Burial network

### 2020-11-02 analysis/paper/paper.Rmd
edit chronology section and adject bootstrap parameters

<!--chronology-->
To compare burial networks, we assigned burials to the pre-European period (n = `r pre_E`), European and post-European period (n = `r post_E`) for network comparison according to depth, radiocarbon dates, diagnostic materials, stratigraphic data, and previous studies. We excluded the burials from the Chinese phase (n = `r chi`) for analysis due to much smaller sample size. Since the sedimentary characteristics show vertical and lateral continuity cross units of AD section, depth is used as the first criterion for burial chronology. The chronology is then evaluated by the burials with light gray glazed jars, also called An-ping jars that were believed to be produced in Southeast China. They circulated in Southeast Asia from the late 16th to 18th century, and often found at sites with the European occupation in the early 17th century in many Aisan places, including Taiwan [@Berrocal2018; @Hsieh1995; @Ketel2011].

In addition to the diagnostic jars, three radiocarbon dates of charcoal associated with three different burials are used as another evidence to evaluate the chronology [@Chen2007]. Some burials that were heavily disturbed by modern construction are excluded to avoid misinterpreting due to incomplete data. With the information of burials, including quantity of grave goods, types of grave goods, burial identities, we can reconstruct social relations between individuals by linking them according to similar prestige goods. This is based on the assumption that the prestige goods imply social practices of trade, exchange, and gifting that reflect social relations between individuals [@Coward2013, pp. 252]. Also, prestige materials usually relate to a representation of social status, where the same economic or social class, tend to use similar goods as a status indicators [citations]. Therefore, we build network where burials represent actors (nodes in the network) that are linked when they have th same prestige goods in common. The prestige goods we identified including agate beads, gold-foil beads, imported Chinese porcelains, gold foils, and fish-shaped ornaments, according to previous research [@Cheng2008; @Hsieh2009; @Hsieh2012; @Wang2011] and the description in historical records [@Borao2009; @LiandWu2006].

>>>>

<!--chronology-->
To compare burial networks, we assigned burials to the pre-European period (n = `r pre_E`), European and post-European period (n = `r post_E`) for network comparison based on established fine-grained chronology that was reexamined and cross-validated by diagnostic materials, stratigraphic data, depth, and radiocarbon dates [@LWandBM2020ornament; @Chen2007]. We excluded the burials from the Chinese phase (n = `r chi`) for analysis due to the smaller sample size. There are eight burials heavily disturbed by modern construction that are excluded to avoid misinterpreting due to distorted chronology. We reconstructed social relations between individuals by linking them according to similar prestige goods. This is based on the assumption that the prestige goods imply social practices of trade, exchange, and gifting that reflect social relations between individuals [@Coward2013, pp. 252]. Also, prestige materials usually relate to a representation of social status because of their limited accessibility that can be used as status indicators [citations]. Therefore, we build networks where burials represent actors (nodes in the network) that are linked when they have the same prestige goods in common. The prestige goods we identified include agate beads, gold-foil beads, imported Chinese porcelains, gold foils, and fish-shaped ornaments that are considered as high-value items by studies across different archaeological contexts [@Cheng2008; @Hsieh2009; @Hsieh2012; @Wang2011] and the description in historical records [@Borao2009; @LiandWu2006].
